Treebeard : An Optimizing Compiler for Tree Based ML Inference

### 2022-04-15 docs/MICRO 2022/tiling.tex
Add draft of uniform tiling
Add prob tiling section

\subsection{Valid Tiling of a Tree}
A tiling $\mathcal{T}$ of the tree $T = (V, E, r)$ with tile size $n_t$ is a partition $\{ T_1, T_2, ... ,T_m \}$ of the set $V$ such that 
\begin{enumerate}
    \item $T_1 \cup T_2 ... \cup T_m = V$
    \item $T_i \cap T_j = \emptyset$ for all $i, j \in [1, m]$ and $i \neq j$
    \item $|T_i| \leq n_t$ for all $i \in [1, m]$
    \item $\forall l \in L$ : $l \in T_i \rightarrow v \notin T_i \;\; \forall v \in V \backslash \{l\}$
    \item Tiles are \textbf{maximal}, i.e. if $|T_i| < n_t$, then there is no $v \in V\backslash \{ T_i \cup L \}$ such that $(u, v) \in E$ for some $u \in T_i$. 
    \item Tiles are \textbf{connected}, i.e. for an $u, v \in T_i$, there is a (undirected) path connecting $u$ and $v$ fully contained in $T_i$.
\end{enumerate}

\TODO{AP We need to talk about how tiling is specified in the compiler}

@@

\subsection{Lookup Table}
A lookup table (LUT) is used to solve the problem described in section \ref{Sec:TileShapesAndDecisionTreeInference}, i.e. given the outcome of the comparisons on all nodes in a tile, determine the child tile we should evaluate next. The LUT is indexed by the tile shape and the comparison outcome. Formally, the LUT is a map.
\[
LUT : (TileShape, < Boolean \times n_t >) \rightarrow [0, n_t] \subset \mathbb{N}
\]

>>>>

\subsection{Valid Tiling of a Tree}
\label{sec:ValidTiling}
A tiling $\mathcal{T}$ of the tree $T = (V, E, r)$ with tile size $n_t$ is a partition $\{ T_1, T_2, ... ,T_m \}$ of the set $V$ such that 
\begin{enumerate}
    \item $T_1 \cup T_2 ... \cup T_m = V$
    \item $T_i \cap T_j = \emptyset$ for all $i, j \in [1, m]$ and $i \neq j$
    \item $|T_i| \leq n_t$ for all $i \in [1, m]$
    \item $\forall l \in L$ : $l \in T_i \rightarrow v \notin T_i \;\; \forall v \in V \backslash \{l\}$
    \item Tiles are \textbf{maximal}, i.e. if $|T_i| < n_t$, then there is no $v \in V\backslash \{ T_i \cup L \}$ such that $(u, v) \in E$ for some $u \in T_i$. 
    \item Tiles are \textbf{connected}, i.e. for an $u, v \in T_i$, there is a (undirected) path connecting $u$ and $v$ fully contained in $T_i$.
\end{enumerate}

@@

\subsection{Lookup Table}
\label{sec:LookupTable}
A lookup table (LUT) is used to solve the problem described in section \ref{Sec:TileShapesAndDecisionTreeInference}, i.e. given the outcome of the comparisons on all nodes in a tile, determine the child tile we should evaluate next. The LUT is indexed by the tile shape and the comparison outcome. Formally, the LUT is a map.
\[
LUT : (TileShape, < Boolean \times n_t >) \rightarrow [0, n_t] \subset \mathbb{N}
\]
